\begin{acknowledgements}

I have been fortunate to work on my Ph.D. surrounded by talented people always willing to help.
The work presented in this thesis certainly would not have been possible without them.
I cannot thank them enough for their support and contributions.

First of all, I would like to thank my advisor, Ivan Bazarov, for guiding me through my experience.
He allowed me to learn, make mistakes, and develop these projects patiently.
I would also like to thank my informal advisors: Jared Maxson and Luca Cultrera. Their expertise and support were invaluable during my Ph.D., and I have learned immensely from them.
Alice Galdi allowed me to ask dumb questions ever since I joined the group and always has been the most approachable senior in the lab.
Tobey Moore has truly magical skills to build anything we ask in time and offered great insights when it comes to designing parts for machines.
Matthew Andorf has been of particular help in the last long project I participated in. It would not have been possible to conclude the project without him.
I would also like to extend special thanks to Adam Bartnik, Dimitri Dimitrov, Oksana Chubenko, Joe Grames, and Marcy Stutzmann for valuable discussions.

Going through a Ph.D. would have been a lot harder without other students around me. After joining the group, William Li and I soon became the only students in the lab. Not only did we learn from each other as we explored the field, but also having another student in the group was tremendous emotional support for me.
I would also like to thank other graduate students, Chad Pennington, Cameron Duncan, Chris Pierce, Mike Kaemingk, and Sam Levenson, for hanging out with me and helping me whenever I ask.

My parents Sung Yeol Bae and Mi Ran Hwang deserve the most thanks of all.

% Chris, Cam, Chad, Mike, Sam
% REU students?
This work was supported by the Department of Energy under grants DE-SC0016203, DE-SC0019122, DE-SC0021039, and the National Science Foundation under grants PHY-1461111, PHY-1549132.

\end{acknowledgements}